High-Dimensional Regularized Discriminant Analysis

### 2016-12-02 reports/paper-hdrda.Rnw
Plots of timing comparisons

TODO

@@

>>>>

TODO
\[ \left[\text{Insert Figure \ref{fig:timing-results} approximately here }\right] \]

\[ \left[\text{Insert Figure \ref{fig:timing-comparison-bootstrap} approximately here }\right] \]

@@

\begin{figure}
<<timing_results, fig.width=8, fig.height=8, dpi=200>>=
p <- ggplot(timings_combined, aes(x=p, y=time, color=Classifier))
p <- p + geom_point() + geom_jitter(width=140, height=0) + facet_wrap(~ Plot, scales="free_y")
p <- p + geom_smooth(method="lm", formula=y ~ poly(x, 2), se=FALSE)
p <- p + scale_color_manual(values=c("#D55E00", "#0072B2"))
p <- p + xlab("Number of Features") + ylab("Model Selection Time (seconds)")
p + theme_bw()
@
\caption{Timing comparisons (in seconds) between HDRDA and RDA classifiers.}
\label{fig:timing-results}
\end{figure}

\begin{figure}
<<relative_timings, fig.width=8, fig.height=8, dpi=200>>=
p <- ggplot(timing_ratios_bootstrap, aes(ratio_means, fill=p))
p <- p + geom_histogram() + facet_wrap(~ p, scale="free_x")
p <- p + xlab("Ratio of Mean RDA Runtime to Mean HDRDA Runtime") + ylab("Bootstrap Replications")
p + theme_bw()
@
\caption{Distribution of ratios of mean \emph{RDA} runtime to mean \emph{HDRDA}
  runtime across 1000 bootstrap replications.}
\label{fig:timing-comparison-bootstrap}
\end{figure}
